% LaTeX file for resume 
% This file uses the resume document class (res.cls)

%\documentclass[margin, 12pt]{res}
\documentclass[margin, line, 12pt]{res} 
%\documentclass[line, 12pt]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{enumitem}

\renewcommand{\namefont}{\Large\textbf}
%\renewcommand{\section}{\large\textbf}

\begin{document} 
 
%\name{Dan Wells\\[12pt]} % the \\[12pt] adds a blank line after name
\name{Dan Wells\smallskip}
%\address{{\Large\bf Dan Wells}}
\address{dan.wells@cantab.net $\diamond$ 07858 506 987}


% Center the name over the entire width of resume:
% \moveleft.5\hoffset\centerline{\Large\bf Dan Wells}
% Draw a horizontal line the whole width of resume:
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
% \moveleft.5\hoffset\centerline{dan.wells@cantab.net $\diamond$ 07858 506 987}
% \moveleft.5\hoffset\centerline{07858 506 987}
 
\begin{resume}

% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}

\section{Education}
{\bf University of Edinburgh}  \hfill 2015 (expected) \\ 
 {\bf MSc Speech and Language Processing} \\ 
{\small Courses include: Automatic Speech Recognition, Speech Synthesis, \\ Machine Translation, Natural Language Understanding,  Topics in NLP, \\ Introductory Applied Machine Learning, Computer Programming, \\ Semantic Web Systems, Univariate Statistics}

{\bf Selwyn College, University of Cambridge} \hfill 2013 \\ 
{\bf BA (Hons) Linguistics} \\
{\small Completed a wide range of studies across all areas of linguistics, with \\ interests especially in phonetics and computational linguistics. \smallskip \\
Additional courses: MML Certificate in Dutch, Introduction to Yiddish} 

{\bf Sandown High School} \hfill 2010 \\
{\small A-levels: Maths (A), Physics (A*), French (A*), English Language(A)\\
AS-levels: Further Maths (A), Fine Art (A)}
 
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}

\section{Experience}
{\bf Google (via Adecco)}  \hfill Jan--Aug 2014 \\
{\bf Speech Data Evaluator} \\
% {\bf Speech Data Evaluator, Google (via Adecco)} \hfill Jan--Aug 2014 \\
Processed linguistic data to improve speech synthesis and automatic \\ speech recognition quality for British English. \smallskip
\begin{itemize}[leftmargin=*] \itemsep -2pt  % reduce space between items
 {\small  
 \item Phonetic transcription of lexicon entries using in-house systems.
\item Transcription of acoustic data following text normalisation guidelines.
\item Quality control for similar work carried out by external vendors.
\item Analysis of ASR system output errors.
 }
 \end{itemize}

{\bf Cambridge Bilingualism Network} \hfill Sep--Oct 2013 \\
{\small  
Encoded a large number of paper surveys on child bilingualism into \\ Excel spreadsheets.
}

% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}

\section{Skills}
{\bf Technical}
\begin{itemize}[leftmargin=*] \itemsep -2pt
{\small
\item Experience programming in Python, some Bash scripting.
\item Acoustic analysis using Praat, Wavesurfer.
\item Comfortable with OS X and Linux operating systems.
\item Typesetting using \LaTeX.
}
\end{itemize}

{\bf Languages} \\
{\small
English: Native speaker. \\
French: Strong reading/writing skills, conversational spoken.
}

\end{resume} 

\end{document} 

